The Skew-Normal Approximation of the Binomial Distribution

### 2010-12-24 pieces/final-paper/output.tex
Renamed graphs -> calculations. Fleshed out README. About to rearrange.

\begin{proof}
  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma^2,
  \lambda)$ is

@@

Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find
estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
and third moments about the mean of $B$ and $Y$.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-least-n.png}
  \caption{Least possible $n$, given a fixed $p$}
  \label{fig:sn-restriction-least-n}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-p-range.png}
  \caption{Range of possible $p$, given a fixed $n$}
  \label{fig:sn-restriction-p-range}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../graphs/images/comparison-n25.png}
  \caption{Binomial, normal, and skew-normal, $n=25$}
  \label{fig:comparison-n25}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../graphs/images/comparison-n50.png}
  \caption{Binomial, normal, and skew-normal, $n=50$}
  \label{fig:comparison-n50}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../graphs/images/comparison-n100.png}
  \caption{Binomial, normal, and skew-normal, $n=100$}
  \label{fig:comparison-n100}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-n.png}
  \caption{MABS as a function of p}
  \label{fig:mabs-fixed-n}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-p.png}
  \caption{MABS as a function of n}
  \label{fig:mabs-fixed-p}
\end{figure}

@@

>>>>

\begin{proof}
  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma,
  \lambda)$ is

@@

Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma, \lambda)$. We will find
estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
and third moments about the mean of $B$ and $Y$.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{../images/restriction-least-n.png}
  \caption{Least possible $n$, given a fixed $p$}
  \label{fig:sn-restriction-least-n}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{../images/restriction-p-range.png}
  \caption{Range of possible $p$, given a fixed $n$}
  \label{fig:sn-restriction-p-range}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../images/comparison-n25.png}
  \caption{Binomial, normal, and skew-normal, $n=25$}
  \label{fig:comparison-n25}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../images/comparison-n50.png}
  \caption{Binomial, normal, and skew-normal, $n=50$}
  \label{fig:comparison-n50}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../images/comparison-n100.png}
  \caption{Binomial, normal, and skew-normal, $n=100$}
  \label{fig:comparison-n100}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../images/mabs-fixed-n.png}
  \caption{MABS as a function of p}
  \label{fig:mabs-fixed-n}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../images/mabs-fixed-p.png}
  \caption{MABS as a function of n}
  \label{fig:mabs-fixed-p}
\end{figure}

@@

\begin{sidewaystable}
  \centering
  \begin{tabular}{ l l l l l l l l l }
    (  0.89,    2.2,   2.31) & (  2.97,   2.94,   1.74) & (  7.44,   3.94,    1.4) & ( 16.77,   5.33,   1.16) \\
    (  3.23,   2.67,    1.5) & (  7.76,   3.61,   1.24) & ( 17.18,   4.89,   1.04) & ( 36.45,   6.68,   0.89) \\
    (   5.8,   2.85,   1.12) & ( 12.86,   3.88,   0.95) & ( 27.31,   5.32,   0.82) & (  56.6,   7.32,   0.72) \\
    (  8.59,   2.83,    0.8) & ( 18.23,   3.89,    0.7) & ( 37.76,   5.39,   0.61) & ( 77.18,   7.48,   0.54) \\
    (  12.5,    2.5,    0.0) & (  25.0,   3.54,    0.0) & (  50.0,    5.0,    0.0) & ( 100.0,   7.07,    0.0) \\
    ( 16.41,   2.83,   -0.8) & ( 31.77,   3.89,   -0.7) & ( 62.24,   5.39,  -0.61) & (122.82,   7.48,  -0.54) \\
    (  19.2,   2.85,  -1.12) & ( 37.14,   3.88,  -0.95) & ( 72.69,   5.32,  -0.82) & ( 143.4,   7.32,  -0.72) \\
    ( 21.77,   2.67,   -1.5) & ( 42.24,   3.61,  -1.24) & ( 82.82,   4.89,  -1.04) & (163.55,   6.68,  -0.89) \\
    ( 24.11,    2.2,  -2.31) & ( 47.03,   2.94,  -1.74) & ( 92.56,   3.94,   -1.4) & (183.23,   5.33,  -1.16) \\
  \end{tabular}
  \caption{foobarbif}
  \label{table:sn-approx-table}
\end{sidewaystable}
